---
output: github_document
---

# Multi-lingual stopwords package in R

**stopwords** is an R package that provides easy access to stopwords in more than 50 languages in the [Stopwords ISO library](https://github.com/stopwords-iso/stopwords-iso). This package should be used conjunction with packages such as [**quanteda**](https://github.com/kbenoit/quanteda) to perform text analysis in many different languages.

## Supported languages

Currently supported languages are the following:

```{r, echo=FALSE, results='asis'}
lang <- stopwords::languages()
cat(paste0('- ', names(lang), ' [', unname(lang), ']\n'))
```

## How to install

Please just execute the following command to install:

```{r, eval=FALSE}
devtools::install_github("koheiw/stopwords")
```

## How to use

The interface of the **stopwords** package is designed to be consistent with **quanteda**, but the words are considerably different:

```{r}
head(quanteda::stopwords('english'), 10)
head(stopwords::stopwords('en'), 10)
```

